Lifting CDCL to Relational Domains

### 2016-10-14 experiments.tex
update section 6
graph added

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains 
in 2LS verification tool~\cite{2ls}.  The abstract domains used for 
our experiments are intervals, template polyhedra, octagons and equalities.  
We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC and a 
commercial static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT 
solver in the backend.  Astr{\'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  To enable precise 
analysis using Astr{\'e}e, all our benchmarks are manually instrumented with 
partition directives which provides external hint to the tool to guide 
the trace partitioning heuristics.  Usually, such high-precision is not 
needed for static analysis, since it makes the analysis very expensive.  
Without trace partitioning, the analysis using Astr{\'e}e shows high 
degree of imprecision.

\paragraph {\em Observation of Analysis}

@@

>>>>

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains 
in 2LS verification tool~\cite{2ls}.  The abstract domains used for 
our experiments are intervals, template polyhedra, octagons and equalities.  
We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC and a 
commercial static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT 
solver in the backend.  Astr{\'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  All the 
bounded loops are completely unrolled in Astr{\'e}e.

\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}
\paragraph {\em Observation of Analysis}

@@

\paragraph {\em \textbf{Propagation Strategy}}
